Public's Ideal Moderation to Online Toxic Speech

### 2024-02-12 paper/paper.qmd
change

---
title: "My title"
author: 
  - Yichen Ji
  - Xiaoxu Liu
thanks: "Code and data are available at: https://github.com/Selinayichenji/Toxic_speech_replication.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
date-format: long
abstract: "In this report,."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

@@

# Introduction

@@

@@

Source
Our replication paper is based on the original paper in American Political Science Review  “Toxic Speech and Limited Demand for Content Moderation on Social Media". Our paper is consistent with the original goal that attempts to find how people respond to toxic speech with different targets to decide the moderation of social media for a respectful and harmonious environment. Our paper applies using the statistical programming language R (R Core Team 2020). Besides the programming tool, we also employ the following packages: readr (Wickham, Hester, and Bryan 2023), broom (找不到), ggplot2 (Wickham H 2016), dplyr (Wickham et al. 2022), tidyverse (Wickham et al. 2019), MetBrewer (找不到), and knitr (Xie 2014).  (unsure about citation)

Methodology
This paper applies the same sources as the original paper does, which consists of Papacharissi (2004, in particular pages 261–7), Herbst (2010), and Boatright et al. (2019); national laws (Busch 2022; European Parliament 2022); Brandeis notes in Whitney v. California 1927, “Partisan Conflict over Content Moderation Is More Than Disagreement about Facts.” (Appel, Pan, and Roberts Reference Appel, Pan and Roberts 2023; Kozyreva et al. Reference Kozyreva, Herzog, Lewandowsky, Hertwig, Lorenz-Spreen, Leiser and Reifler 2023), BBC. 2012. “Reddit Will Not Ban ‘Distasteful’ Content, Chief Executive Says”, Bejan, Teresa M. 2017. Mere Civility. Cambridge, and so on.

measurement

# Results {#sec-result}

@@

```{r}
#| echo: false
#| warning: false
#| message: false

#### Loading the Cleaned Dataset ###

@@

```{r lgbtq_rep, fig.width=6, fig.height=5.1}
#| echo: false
#| eval: true
#| warning: false

@@

>>>>

---
title: "Public's Ideal Moderation to Online Toxic Speech"
author: 
  - Yichen Ji
  - Xiaoxu Liu
thanks: "Code and data are available at: https://github.com/Selinayichenji/Toxic_speech_replication.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
date-format: long
abstract: "In this report,we analysis the public's ideal moderation for 5 levels toxic online speech.It was found that most people tend not to give harsh moderations, unless the speech touches upon personal threat. And people with different social factors have difference preferences on moderations.The findings will help me build a ideal standard platform for the public."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

```{r setup}
#| include: false
#| warning: false
#| message: false

@@

# Introduction
*This reproduction was performed after a replication on the Social Science Reproduction platform:****[link here](https://www.socialsciencereproduction.org/reproductions/f4c25f83-2c8b-448e-be76-760e02694112/index)***

@@

ESTIMATE

@@

## Source

Our replication paper is based on the original paper in American Political Science Review  “Toxic Speech and Limited Demand for Content Moderation on Social Media". Our paper is consistent with the original goal that attempts to find how people respond to toxic speech with different targets to decide the moderation of social media for a respectful and harmonious environment.

This paper applies the same sources as the original paper does, which consists of Papacharissi (2004, in particular pages 261–7), Herbst (2010), and Boatright et al. (2019); national laws (Busch 2022; European Parliament 2022); Brandeis notes in Whitney v. California 1927, “Partisan Conflict over Content Moderation Is More Than Disagreement about Facts.” (Appel, Pan, and Roberts Reference Appel, Pan and Roberts 2023; Kozyreva et al. Reference Kozyreva, Herzog, Lewandowsky, Hertwig, Lorenz-Spreen, Leiser and Reifler 2023), BBC. 2012. “Reddit Will Not Ban ‘Distasteful’ Content, Chief Executive Says”, Bejan, Teresa M. 2017. Mere Civility. Cambridge, and so on.

Similar dataset

## Methodology

Our paper applies using the statistical programming language R [@citeR]. Besides the programming tool, we also employ the following packages: readr [@read], broom [@broom], ggplot2 [@gg2], dplyr [@dpr], tidyverse [@tidy], MetBrewer [@met], and knitr [@citeknr].

## Variables
We only introduced the variables used in our own analysis. For the full variables from the original paper, please check the Appendix.

- Treatment: non-group-related control, control, uncivil, intolerant and threatening.
   - Non-group-related control means no target and no toxic language.
Control means anti-target but without the 3 kinds of toxic languages: uncivil, intolerant and threatening. 
In original paper, uncivil is defined as "including anything from an unnecessarily disrespectful tone and lack of respect to rudeness and inconsiderate language."[@paper]. 
And the intolerance differs from incivility, "it aims to derogate, silence, or undermine particular groups due to their protected characteristics, attack their rights, and incite violence and harm."[@paper].
The threatening is a toxic behavior explicitly announces the intention of physical harm.[@paper].

- Handle: (1) Leave it, do nothing; (2) Place a warning label on the post; (3) Reduce how many people can see the post; (4) Permanently remove the post; (5) Suspend the person’s account.

- Gender: Male, Female and Others.
- Education: High school graduate; College; Postgraduate.
- Race: White, Black, Hispanic and Others.
- Percentage: It means the ratio of 5 handles given by people with the same social factor when they are facing the same treatment.

## Measurement
The data collected by using survey.

## Structure of the paper'remainder parts

\newpage
# Results {#sec-result}

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#### Loading the Cleaned Dataset ###

@@

```{r, fig.width=6, fig.height=5.1}
#| echo: false
#| eval: true
#| label: fig-lgbtq-rep
#| warning: false

@@

@fig-lgbtq-rep
